\section{7.2.A.}\label{Rising Sea 7.2.A.}

\textit{MORPHISMS OF RINGED SPACES GLUE}.
\begin{proof}
    For topological map $f$, the existence is clear (existence and the restriction will behave as desired). It remains to define the morphism of sheaves $$f^{\sharp}:\mathscr O_Y\to \pi_{\ast}\mathscr O_X$$ and check that $(\pi\vert_{U_i})^{\sharp}:\mathscr O_Y\to (\pi\vert_{U_i})_{\ast}\mathscr O_{U_i}=\pi_i^{\sharp}:\mathscr O_Y\to \pi_{i,\ast}\mathscr O_{U_i}$.

    By assumption, we have $\{\pi_i~:~U_i\to Y\}_{i\in \bullet}$ with $\pi_i^{\sharp}:\mathscr O_Y\to \pi_{i,\ast}\mathscr O_{U_i}$ for each $i\in\bullet$. Also recall that 
    \begin{align*}
        (\pi_i\vert_{U_i\cap U_j})^{\sharp}:&~\mathscr O_Y\to (\pi_i\vert_{U_i\cap U_j})_{\ast}\mathscr O_{U_i\cap U_j}= \\
        (\pi_j\vert_{U_i\cap U_j})^{\sharp}:&~\mathscr O_Y\to (\pi_j\vert_{U_i\cap U_j})_{\ast}\mathscr O_{U_i\cap U_j}.
    \end{align*}Therefore for any open subset $W\subset Y$, we have $(\pi_i\vert_{U_i\cap U_j})^{\sharp}(W)=(\pi_j\vert_{U_i\cap U_j})^{\sharp}(W)$. In particularly, we have 
    \begin{align*}
        (\pi_i\vert_{U_i\cap U_j})_{\ast}\mathscr O_{U_i\cap U_j}(W) =&~ \mathscr O_{U_i\cap U_j}((\pi_i\vert_{U_i\cap U_j})^{-1}(W))\\
        =&~ \mathscr O_{U_i\cap U_j}(\pi_i^{-1}(W)\cap U_i\cap U_j)\\
        =&~ \mathscr O_{X}(\pi_i^{-1}(W)\cap U_i\cap U_j)\\
        =&~ \mathscr O_X(\pi_j^{-1}(W)\cap U_i\cap U_j)\\
        =&~ (\pi_j\vert_{U_i\cap U_j})_{\ast}\mathscr O_{U_i\cap U_j}(W). 
    \end{align*}

    Now we need to define $\pi^{\sharp}:\mathscr O_Y\to \pi_{\ast}\mathscr O_X$. For every open subset $W\subset Y$, we have to define a map
    \[\pi^{\sharp}(W):\mathscr O_Y(W)\to \pi_{\ast}\mathscr O_X(W).\]
    For every $s\in \mathscr O_Y(W)$, we define(at this moment, we've constructed topologically the map $\pi$)
    \begin{align*}
        s_i:=\pi_i^{\sharp}(W)(s)=&~(\mathscr O_Y(W)\to \pi_{i,\ast}\mathscr O_{U_i}(W))(s)\\
        \in&~\mathscr O_X(\pi_i^{-1}(W)\cap U_i)=\mathscr O_X(\pi^{-1}(W)\cap U_i)
    \end{align*}
    We can check 
    \begin{align*}
        s_i\vert_{\pi^{-1}(W)\cap U_i\cap \pi^{-1}(W)\cap U_j}=&~ (\mathscr O_X(\pi^{-1}(W)\cap U_i)\to\mathscr O_X(\pi^{-1}(W)\cap U_i\cap U_j))(s_i)\\
        =&~ (\mathscr O_X(\pi_i^{-1}(W)\cap U_i)\to\mathscr O_X(\pi_i^{-1}(W)\cap U_i\cap U_j))(s_i)\\ 
        =&~ (\mathscr O_Y(W)\to \mathscr O_X(\pi^{-1}(W))\to \mathscr O_X(...))(s)\\
        =&~ (\mathscr O_X(\pi_j^{-1}(W)\cap U_j)\to\mathscr O_X(\pi_j^{-1}(W)\cap U_i\cap U_j))(s_j)\\  
        =&~ s_j\vert_{\pi^{-1}(W)\cap U_i\cap \pi^{-1}(W)\cap U_j}
    \end{align*}

    Notice that we have $\{\pi^{-1}(W)\cap U_i\}_{i\in\bullet}$ covers $\pi^{-1}(W)$ and $\mathscr O_X$ is a sheaf. Therefore there exist $S\in \mathscr O_X(\pi^{-1}(W))=\pi_{\ast}\mathscr O_X(W)$ such that $S\vert_{U_i}=s_i$. Hence for every $W\subset Y$ we've defined the map $\pi^{\sharp}$. And we can check that for all open subsets $W\subset U_i$, \[(\pi\vert_{U_i})^{\sharp}(W)=\pi_i^{\sharp}(W)\Rightarrow(\pi\vert_{U_i})^{\sharp}=\pi_i^{\sharp}.\]
    \todo{???}
\end{proof}

\subsection{Comments}
See Prop 3.5. \cite{gortz2020algebraic} on Page 70. For details, see \href{https://math.stackexchange.com/questions/442911/glueing-morphisms-of-sheaves-together-can-i-just-do-this}{\enquote{Glueing morphisms of sheaves together - can I just do this?}} and \href{https://math.stackexchange.com/questions/1173973/morphism-of-ringed-spaces-glue?noredirect=1&lq=1}{\enquote{morphism of ringed spaces glue}}.
\section{7.2.D.}

\begin{exercise}[Pulling Back $\mathscr O$-module]
    Suppose $\pi:(X,\mathscr O_X)\to (Y,\mathscr O_Y)$ is a morphism of ringed spaces. A slight variation on the inverse image allows us to pull back an $\mathscr O_Y$-moudle $\mathscr G$ to get an $\mathscr O_X$-module $\pi^{\ast}\mathscr G$.
    
\end{exercise}
\subsection{(a)}
\begin{align}
    (X,\mathscr O_X)\overset{\pi_1}{\to}(X,\pi^{-1}\mathscr O_Y)\overset{\pi_2}{\to} (Y,\mathscr O_Y)
\end{align}
With the notation displayed as above, we need to firstly define $\pi_1,\pi_2$ and then check the commutativity. Both definition and checking commutativity involves both the topological maps as well as pullback of corresponding sheaves.

\begin{enumerate}
    \item Now we'll define two morphisms 
    \begin{enumerate}
        \item For $\pi_1$. We take the identity map $\id_{X}$ over $X$ to be the topological map; it remains to define
        \[\pi^{-1}\mathscr O_Y\to \pi_{1,\ast}\mathscr O_X\]
        Fix $U\subset X$, and we let $V_1\supset V_2\supset \pi(U)$ inside $Y$.
        \[% https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBpiBdUkANwEMAbAVxiRAB12BbOnACzgBjAE4ACAPIB9AJoAKAGqSAjAEoQAX1LpMufIRRLyVWoxZtOPfkLFS5igExrN27HgJEyS4-WatEHbl4BEQlJAA1ZTjQsAD1gAFoldQVlFSctEAxXPSJDL2ofM38LIOtQiKjYhKSUx3SXXXcUe1J8k19zdmjJYENOOjgcdRKrEKkIgFUVAF4R4Jtw2SmNDKzG-WQWygLTPwDouMThwNGFuSnZk4EAM2AAYQgGLC51HvlOOCY0OBgcUUqlip1P8rmVbAonMYYFAAObwIiga7CCBcJBkEA4CBIJIZJEotHUTFIezOEB41GIQwYrGIADMpPJxMJNPpuORFIArMykAAWBnspC07mIPls-GU4Uc9QUdRAA
        \begin{tikzcd}
        \mathscr O_Y(V_1) \arrow[r] \arrow[d] & \mathscr O_Y(V_2) \arrow[d] \arrow[r] & \pi^{-1}\mathscr O_Y(U)=\mathsf{Colim}_{V\supset \pi(U)} \mathscr O_Y(V) \arrow[d] \\
        \mathscr O_X(\pi^{-1}(V_1)) \arrow[r] & \mathscr O_X(\pi^{-1}(V_2)) \arrow[r] & {\pi_{1,\ast}\mathscr O_X(U)=\mathscr O_X(U)}                                   
        \end{tikzcd}\]
    \item For $\pi_2$. We take $\pi$ to be the topological map. Hence we would like to unwrap the definition of 
    \begin{align}
        \mathscr O_Y\to \pi_{2,\ast}\pi^{-1}\mathscr O_Y.
    \end{align}
    For $W\subset Y$, we simply use the canonical map to the colimit (induced by the universal property of colimit) 
    \begin{align}
        \mathscr O_Y(W)\to &~\pi_{2,\ast}\pi^{-1}\mathscr O_Y(W)\\ 
        =&~\pi^{-1}\mathscr O_Y(\pi^{-1}(W))\\
        =&~\Colim _{V\supset \pi(\pi^{-1}(W))}\mathscr O_Y(V)\\
        =&~\Colim _{V\supset W}\mathscr O_Y(V).
    \end{align}
    \end{enumerate}
    \item We check the commutativity. For topological space $\pi_1,\pi_2$ together work well. For the sheaf morphism, we intend to check two morphisms are isomorphic:
    \begin{align}
    \phi_1:&~\mathscr O_Y\to \pi_{\ast}\mathscr O_X=\\
    \phi_2:&~\mathscr O_Y\to \pi_{2,\ast}(\pi^{-1}(\mathscr O_Y))\to \pi_{2,\ast}\pi_{1,\ast}\mathscr O_X.
    \end{align}
    We could do this by checking for arbitrary $W\subset Y$, 
    \begin{align}
        \phi_{1}(W)=&~\mathscr O_Y(W)\to \pi_{\ast}\mathscr O_X(W)\\
        \phi_{2}(W)=&~\mathscr O_Y(W)\to \ldots \to \pi_{\ast}\mathscr O_X(W).
    \end{align}
    Therefore we obtained the commutativity for the sheaves. 
\end{enumerate}

\begin{remark}
    For composition of morphism in ringed spaces, see this \href{https://math.stackexchange.com/questions/611497/does-hartshorne-really-not-define-things-like-the-composition-or-restriction-o}{post}.
\end{remark}

\section{7.2.E.}

See Hartshorne \cite{hartshorne2013algebraic} Page 72 for details.

\section{7.3.A.}

For a local homomorphism, we have 
\[\mathfrak m_{q}\subset \mathscr O_{Y,q}\to \mathscr O_{X,p}\to\kappa (p).\]It will induce a map $\kappa(q)\to\kappa(p)$.

\section{7.3.B.}

\section{7.3.D.}

!
\section{7.3.F.}

\begin{itemize}
    \item See this \href{https://gemini.google.com/share/11c266ac4484}{conversation} with Gemini. 
    \item See Remark 3.15.~\cite{gortz2020algebraic}
\end{itemize}


\section{7.3.G.}

See \cite{gortz2020algebraic} Proposition 3.4. Chap 3 on Page 69.

See \href{https://stacks.math.columbia.edu/tag/01I1}{Tag 01I1}.
\section{7.3.6.}

For \enquote{fun question}: is that maximalSpec?
\section{7.3.O.}
See \href{https://gemini.google.com/share/b1e4a38864db}{conversation} with Gemini.

\section{7.3.L.}

Nice hint. See Hartshorne Chap 2 Exercise 2.7. \cite{hartshorne2013algebraic}.

\section{7.4.}

Skipped\dots

\section{7.5.B.}

\href{https://stacks.math.columbia.edu/tag/0CC1}{Tag 0CC1}

\section{7.5.4.}

Gathmann's notes Definition 9.5 provided the proof, with one subtlety missed.
See \href{https://gemini.google.com/share/99bbf881ad18}{Gemini: Dominant Maps and Rational Map Composition}


