\section{Lemma 3.1.}

See Sandor's Notes Lecture 4, Lemma 2.6.

Closedness can be checked locally. See a post \href{https://math.stackexchange.com/questions/717382/how-to-prove-that-z-is-closed-subset-iff-x-can-be-covered-by-open-subsets}{HERE}.

\subsection{Closedness local criterion}

This is HW 2.3. of Sandor's notes. 

\textit{Let $X$ be a topological space and $W \subset X$ a subset. Then $W$ is closed if and only if for every $P\in X$ there is an open subset $U \subset X$ such that $P \in U$ and $W \cap U \subset U$ is a closed subset in $U$.}

\begin{proof}
	Assume $W$ is closed, we can simply take $U=X$ for any $P$.

	Conversely, we only need to verify that $X\setminus W$ is open. More precisely, we wish to prove that every point $P\in X\setminus W$ has an open neighborhood that contains in $X\setminus W$. This is ensured by Proposition 2.8. on Page 24 of \cite{lee2010introduction}. 

	Now start with an arbitrary point $q\in X\setminus W$, there exists open subset $U_q$ of $X$ such that \[W\cap U_q\subset U_q\] is closed in $U_q$. Then we can take $U_q\setminus W$ as the open neighborhood of $q$ in $X\setminus W$ as expected. Hence we know $X\setminus W$ is open.
\end{proof} 

\section{Remark 3.1.1.}

See Sandor's Notes Lecture 5, Corollary 2.10.
Notice that Hartshorne defined variety to be irreducible.
See a post explaining why the preimage is dense \href{https://math.stackexchange.com/questions/2860498/regular-functions-are-determined-only-up-to-open-sets#:~:text=An%20important%20consequence%20of%20this,dense%2C%20hence%20equal%20to%20X.}{HERE}.

See Lemma 14. on Page 210 of \cite{bosch2013algebraic}.

\section{Definition: Ring of Regular Function}
\href{https://www2.math.ethz.ch/education/bachelor/lectures/fs2016/math/alg_geom/Solution8.pdf}{HERE} is an explicit description on the ring structure of $\mathcal O_{P,Y}$.

\section{Theorem 3.2.}

See S\'andor's Lecture Notes 09, STEP 03.
See solution of problem 3 \href{https://www2.math.ethz.ch/education/bachelor/lectures/fs2016/math/alg_geom/Solution8.pdf}{HERE}.
See a post \href{https://math.stackexchange.com/questions/1337842/with-regards-to-theorem-3-2-in-hartshorne-are-regular-functions-on-a-variety-si}{HERE}, \href{https://math.stackexchange.com/questions/1909153/some-questions-on-hartshornes-theorem-i-3-2}{HERE}.

\subsection{(c)}
\textit{for each $P$, $\mathcal O_P\cong A(Y)_{\mathfrak m _P}$, and $\operatorname{dim}\mathcal O_P=\operatorname{dim} Y$; }

\begin{proof}
We begin with an injective homomorphism $\alpha:A(Y)\to \mathcal O(Y)$.
And we define a map 
\begin{align*}
    A(Y)_{\mathfrak m_P} &\to \mathcal O_{P,Y}\\
    f/g &\mapsto \langle V,\frac{\alpha(f)}{\alpha(g)}\rangle
\end{align*}where $\frac{\alpha(f)}{\alpha(g)}\in\mathcal O(V)$. 
Now we wish to give an explicit description of $V$.
Since $\alpha(f)\in\mathcal O(Y)$, we know there exists an open subset $P\in V_1\subset Y$ such that 
\[\alpha(f)\mid_{V_1}=\frac{h_1}{h_2}\mid_{V_1}\] where $h_1,h_2\in A$ and $0\notin h_2(V_1)$.
Since $\alpha(g)\in\mathcal O(Y)$, we know there exists an open subset $P\in V_2\subset Y$ such that 
\[\alpha(g)\mid_{V_2}=\frac{h_3}{h_4}\mid_{V_2}\] where $h_3,h_4\in A$ and $0\notin h_4(V_2)$.
Here $g\notin \mathfrak m_P$ by definition of localisation, which gives us 
\[g(P)\neq 0 ~\Rightarrow~ \alpha(g)(P)\neq 0 ~\Rightarrow~ ~\exists~ V_3\subset Y,~ \alpha(g)\mid_{V_3}\neq 0.\] 
Then we take $V=V_1\cap V_2\cap V_3$ will suffice to work. This is because for any point $P\in V$, we have 
\[\frac{\alpha(f)}{\alpha(g)}=\frac{h_1h_4}{h_2h_3}\] for $0\notin h_2h_3(V)$.

% https://q.uiver.app/#q=WzAsNCxbMSwwLCJcXG1hdGhjYWwgTyhZKSJdLFswLDAsIkEoWSkiXSxbMiwwLCJcXG1hdGhjYWwgT197UCwgWX0iXSxbMSwxLCJBKFkpX3tcXG1hdGhmcmFrIG1fUH0iXSxbMSwwLCJcXGFscGhhIl0sWzAsMiwiIiwwLHsic3R5bGUiOnsidGFpbCI6eyJuYW1lIjoiaG9vayIsInNpZGUiOiJ0b3AifX19XSxbMSwzXSxbMywyLCIiLDIseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJkYXNoZWQifX19XV0=
\[\begin{tikzcd}
	{A(Y)} & {\mathcal O(Y)} & {\mathcal O_{P, Y}} \\
	& {A(Y)_{\mathfrak m_P}}
	\arrow["\alpha", from=1-1, to=1-2]
	\arrow[hook, from=1-2, to=1-3]
	\arrow[from=1-1, to=2-2]
	\arrow[dashed, from=2-2, to=1-3]
\end{tikzcd}\]
The induced map is given by universal property of localisation, for every elements in $A(Y)\setminus \mathfrak m_{P}$ will be mapped to a unit in $\mathcal O_{P,Y}$. 
And the map given by Lecture Notes 09 of Prof. S\'andor satisfy the universal property (it makes the diagram commute and maps elements outside of $\mathfrak m_P$ to units).

\end{proof}

\section{Proposition 3.3.}

See a post \href{https://math.stackexchange.com/questions/787770/hartshorne-propositon-i-3-3}{HERE}.

\section{Lemma 3.6.}

See a post \href{https://math.stackexchange.com/questions/457328/hartshorne-lemma-i-3-6}{HERE}.

Here are some details for proving $x_i\circ \psi$ being regular implies $\psi$ is a morphism:
Coordinate functions means 
\[\psi(p)=(\psi_1(p),\psi_2(p),...,\psi_n(p))\in Y\subset \mathbb A^n\] for any $p\in X$.
Firstly, we check $\psi$ is continuous. Take any closed subset $Z(f_1,...,f_r)\subset Y$ for some polynomial $f_1,...,f_r\in A=k[x_1,...,x_n]$. We can compute the preimage as \begin{align*}
    \psi^{-1}(Z(f_1,...,f_r)) =& \{~ p\in X ~\mid ~\forall~ p\in X,~ f_i\circ \psi(p)=0 ~\}.
\end{align*}
Notice that for any $p\in X$, \[f_i\circ \psi(p) ~=~ f_i(\psi_i(p),...,\psi_n(p))\] is continuous since $f_i$ is a polynomial and each $\psi_i:=x_i\circ \psi$ is continuous by assumption that they're regular.
Notice that the preimage of $\psi$ is precisely intersection of $\psi_i^{-1}(\{0\})$ where $1\leq i\leq n$. Hence the preimage is closed, and it follows that $\psi$ is continuous as expected. 

Secondly, fix an arbitrary open subset $V\subset Y$ with an arbitrary regular function $g:V\to k$, we wish to prove $g\circ \psi:\psi^{-1}(V)\to k$ is regular. For any $\psi(p)\in V$ with some $p\in X$, there exists a neighborhood $\psi(p)\in U\subset Y$ such that $g$ equals to an expression of quotients of polynomial, i.e. \[g=\frac{g_1}{g_2}\] where $g_1,g_2\in A$. Then for $p\in X$, take the open neighborhood of it as $\psi^{-1}(U)$, we can see 
\[g\circ \psi (p) = \frac{g_1(\psi(p))}{g_2(\psi(p))}.\]

\section{Exercise 3.5.}

\subsection{Hint}
See a post \href{https://math.stackexchange.com/questions/538136/complements-of-hypersurfaces-in-a-projective-space-is-affine}{HERE}.

\section{Exercise 3.6.}

See a post \href{https://math.stackexchange.com/questions/2120717/there-are-quasi-affine-varieties-which-are-not-affine#:~:text=I%20see%20this%20sentence%20in,(0%2C0)%7D.}{HERE}.

\section{Exercise 3.7.}

See this \href{https://math.stackexchange.com/questions/699433/exercise-3-7-hartshorne}{POST}.

\section{Exercise 3.10. \textbf{Subvarieties}}

\subsection{Locally Closed} 

See Wiki's notes \href{https://en.wikipedia.org/wiki/Locally_closed_subset}{HERE}. 

See a post \href{https://math.stackexchange.com/questions/341665/image-of-a-morphism-of-varieties}{HERE}: image of a variety can be not even locally-closed.

\section{Exercise 3.17.}
\textit{\textbf{Normal Varieties.} A vareity $Y$ is \textbf{normal at a point} $P\in Y$ if $\mathscr O_p$ is an integrally closed ring. $Y$ is \textbf{normal} if it is normal at every point.}

\subsection{(a)}\textit{Show that every conic in $\mathbb P^2$ is normal.}

\begin{proof}
According to Exercise 1.1.(c), we assume conic $Y$ in $\mathbb P^2_{x,y,z}$ is defined by an irreducible homogeneous polynomial of degree $2$. 

And by Exercise 3.1.(c) we know every conic in $\mathbb P^2$ is isomorphic to $\mathbb P^1$. To check it's normal, we need to show for any $P\in Y=\mathbb P^1$, the local ring $\mathscr O_P$ is an integrally closed ring. 

Note that
\[\mathscr O_{P,\mathbb P^1}\simeq \mathscr O_{P,\mathbb A^1}=A(\mathbb A^1)_{\mathfrak m_P}=(k[x])_{\mathfrak m_P}.\] While $k[x]$ is integrally closed, so we know its localisation is integrally closed hence every conic in $\mathbb P^2$ is normal. ???

Or we can use Exercise 3.18 (a). Notice that the homogeneous coordinate ring $S(\mathbb P^1)$ is clearly integrally closed, then it's projectively normal therefore normal.?

\end{proof}

\subsection{(b)}
\textit{Show that the quadric surfaces $Q_1,Q_2$ in $\mathbb P^3$ given by equations $Q_1: xy-zw$; $Q_2:xy=z^2$ are normal (cf. (II. Ex. 6.4) for the latter.)}

\begin{proof}
	Denote $Q_1=Z(xy-zw)\subset \mathbb P^3_{x,y,z,w}$. We have to compute the localisation of its homogeneous coordinate ring at some point $P\in Q_1$
	\begin{align*}
		\mathscr O_P =& S(Q_1)_{(\mathfrak m_P)}\\
		=& (k[x,y,z,w]/I(Q_1))_{(\mathfrak m_P)}\\
		=& (k[x,y,z,w]/\langle xy-zw\rangle)_{(\mathfrak m_P)}\\
	\end{align*}
	It suffices to check the quotient ring
	\[k[x,y,z,w]/\langle xy-zw\rangle \] is an integrally closed ring.???\\\\

	Another approach is to use Jacobian matrix to check it's "smooth $\Rightarrow$ regular $\Rightarrow$ normal". Dimension of a surface is $2$, then $n-r=4-2=2\geq 1$. Here $1$ is the rank of Jacobian matrix at any point on the surface (for we choose only one polynomial $xy-zw$ as generator for $I(Q_1)$). 

	Similarly we can check for $Q_2$.

\end{proof}

\subsection{(c)}
\textit{Show that the cuspidal cubic $y^2=x^3$ in $\mathbb A^2$ is not normal.}

\begin{proof}
	Let $P=(0,0)$, we wish to show that the local ring $\mathscr O_P$ is not integrally closed. Let $X=Z(y^2-x^3)$, and note that $y^2-x^3$ is irreducible in $k[x,y]$.
	\begin{align*}
		\mathscr O_P =& A(X)_{\mathfrak m_P} = k[x,y]/I(X)_{\mathfrak m_P}=k[x,y]/(y^2-x^3)_{\mathfrak m_P}.
	\end{align*}
	While integrally closed is a local property, it's equivalent to check $k[x,y]/(y^2-x^3)$ is an integrally closed domain. Since $y^2-x^3$ is irreducible in UFD, then this quotient ring an integral domain. Denote $R=k[x,y]/(y^2-x^3)$. Notice that $y/x\in \operatorname{Frac}(R)$ is an integral element since 
	\[(y/x)^2-x=0\in R.\] On the other hand, the element $y/x\notin R$. Because otherwise we'll have $y/x=f$ for some polynomial $f\in R$, which is an integral domain. In integral domain, the difference between the degree of variables will give a contradiction. Hence $k[x,y]/(y^2-x^3)$ isn't integrally closed ring.
\end{proof}

See a post \href{https://math.stackexchange.com/questions/880433/is-mathbbcx-y-y2-x3-a-pid}{HERE}, \href{https://math.stackexchange.com/questions/2701183/the-following-domain-is-not-integrally-closed-mathbb-cx-y-langle-y2-x3}{HERE}.

\subsubsection{Hint}

According to Example 2 of Chapter 9 on Integral Extension on Page 65 of \cite{matsumura1989commutative}, we know 
\[k[x,y]/\langle y^2-x^3\rangle\sim k[t^2,t^3]\subsetneq k[t].\] Hence it's not an integrally closed domain.

\subsection{(d)}
\textit{If $Y$ is affine, then $Y$ is normal $\Leftrightarrow$ $A(Y)$ is integrally closed.}

\begin{proof}
	For $Y$ affine, we have $Y$ being normal is equivalent to say $\mathscr O_{P,Y}=A(Y)_{\mathfrak m_P}$ is integrally closed for any point $P\in Y$. While being integrally closed is a local property, it's equivalent to say $A(Y)$ is integrally closed.
\end{proof}

\subsection{(e)}
\textit{Let $Y$ be an affine variety. Show that there is a normal affine variety $\widetilde Y$, and a morphism $\pi: \widetilde Y\to Y$, with the property that whenever $Z$ is a normal variety, and $\varphi:Z\to Y$ is a \textbf{dominant} morphism (i.e., $\varphi(Z)$ is dense in $Y$), then there is a unique morphism $\theta:Z\to \widetilde Y$ such that $\varphi=\pi\circ\theta$. $\widetilde Y$ is called the \textbf{normalization} of $Y$. You will need (3.9A) above.}

\begin{proof}
	Use Prof. S\'andor's notes on Lecture 29 Theorem 4.16.

	To complete the proof, we have to check the pre-variety defined in the proof is actually a variety. ?
\end{proof}

\section{Exercise 3.18.}
\textit{\textbf{Projectively Normal Varieties.} A projective variety $Y\subset \mathbb P^n$ is \textbf{projectively normal} (with respect to the given embedding) if its homogeneous coordinate ring $S(Y)$ is integrally closed.}

\subsection{(a)}
\textit{If $Y$ is projectively normal, then $Y$ is normal.}

\begin{proof}
Since $Y$ is projectively normal, then we know $S(Y)$ is integrally closed. Then we need to show 
\[\mathscr O_P=S(Y)_{(\mathfrak m_P)}\] is integrally closed. Clearly, $S(Y)_{\mathfrak m_P}$ is integrally closed. By definition we know $\mathscr O_P=S(Y)_{(\mathfrak m_P)}$ is a subring composed of degree $0$ elements in $\mathscr O_P=S(Y)_{\mathfrak m_P}$. It is again integrally closed for any element $f/g\in \mathscr O_P=S(Y)_{\mathfrak m_P}$ that is integral over $\mathscr O_P=S(Y)_{(\mathfrak m_P)}$ satisfy the following equations 
\[(f/g)^n+a_{n-1}(f/g)^{n-1}+a_0=0\] for some $a_{i}\in \mathscr O_P=S(Y)_{(\mathfrak m_P)}$ where $0\leq i\leq n-1$. Taking degree function on both sides, then it follows that $f/g$ must be of degree $0$, hence $\mathscr O_P=S(Y)_{(\mathfrak m_P)}$ is integrally closed. 

\end{proof}

\subsection{(b)}
\textit{}


\section{Exercise 3.20.}
\textit{Let $Y$ be a variety of dimension $\geq 2$, and let $P\in Y$ be a normal point. Let $f$ be a regular function on $Y-P$.}

See a post \href{https://math.stackexchange.com/questions/1791250/regular-functions-extension-to-normal-points-of-varieties}{HERE}. 

\subsection{(a)}