
\section{Definition: Irreducible}

For equivalent definitions, see Wiki \href{https://en.wikipedia.org/wiki/Irreducible_component}{HERE};
Also see "dense" on Wiki \href{https://en.wikipedia.org/wiki/Dense_set}{HERE}.

See Atiyah's \cite{atiyah1994introduction} Exercise 19 from Chapter 1 for more information...

See Lemma 14. on Page 210 of \cite{bosch2013algebraic} for equivalent characterisation of \textit{irreducible}.

\section{Example 1.1.3.}
See Atiyah's \cite{atiyah1994introduction} Exercise 19 from Chapter 1, which proves it must be dense.

For the sake of contradiction, assume a non-empty subset $A\subset X$ is reducible. Hence there exist two proper closed subset $A_1,A_2\subset A$ such that $A=A_1\cup A_2$.
Then we have $$X=(A^c\cup A_1)\cup (A^c\cup A_2),$$ which implies $X$ is reducible. \todo{\ding{53}!}
\subsection{}
See a post \href{https://math.stackexchange.com/questions/460074/an-open-subset-of-an-irreducible-set-is-dense}{HERE} \todo{\ding{52}}

First approach applied some density argument. While the second approach, similarly, gave a decomposition of the whole space given the open set is reducible.

\section{Example 1.1.4.}

See Atiyah's \cite{atiyah1994introduction} Exercise 20 from Chapter 1.

\section{Definition.} 
"Induced topology". Definition of \textit{quasi affine variety}, see \href{https://math.stackexchange.com/questions/1086839/a-confusion-regarding-the-definition-of-a-quasi-affine-variety}{HERE}.

\section{Prop 1.2 (d)}

According to Hilbert's Nullstellensatz, I agree we'll get $I(Z(\mathfrak a))\subset \sqrt{\mathfrak a}$.
For the reverse inclusion, pick any $f\in A$ such that $f^r\in\mathfrak a$ where $r\in\mathbb Z_{>0}$. We wish to show that $f(P)=0$ for any $P\in Z(\mathfrak a)$. By definition, $f^r(P)=0$ given $f^r\in\mathfrak a$. And this implies $$f^r(P)=(f(P))^r=0 ~\Rightarrow~ f(P)=0$$ given the polynomial ring $A$ is an integral domain. Therefore we get the inclusion 
$$I(Z(\mathfrak a))\supset \sqrt{\mathfrak a}.$$

See Theorem 6 on Page 183, Strong Nullstellensatz, \cite{cox2013ideals}. \todo{\ding{52}}

\section{Theorem 1.3A. Hilbert's Nullstellensatz}

For the case where $k$ isn't algebraically closed, see \cite{reid1995undergraduate} Remarks in 5.6.

\subsection{}

For the proof, see \cite{kemper2011course} Chapter 1 for details.

The followings are some comments for \cite{kemper2011course} Chapter 1 Theorem 1.7.

A post on surjective preimage for maximal ideal \href{https://math.stackexchange.com/questions/1198414/pull-back-image-of-maximal-ideal-under-surjective-ring-homomorphism-is-maximal}{HERE}.

A post on preimage for maximal ideal (not necessarily surj) \href{https://math.stackexchange.com/questions/882524/in-an-extension-of-finitely-generated-k-algebras-the-contraction-of-a-maximal}{HERE}.

For completeness, a post on preimage of prime ideals \href{https://math.stackexchange.com/questions/409999/prove-that-the-preimage-of-a-prime-ideal-is-also-prime}{HERE}.

A post on image of prime ideals \href{https://math.stackexchange.com/questions/1805457/how-to-prove-that-the-image-of-a-prime-ideal-is-also-a-prime-ideal}{HERE}, \href{https://math.stackexchange.com/questions/292829/a-proof-that-shows-surjective-homomorphic-image-of-prime-ideal-is-prime}{HERE}, and \href{https://math.stackexchange.com/questions/1144695/assume-p-is-a-prime-ideal-s-t-k-subset-p-show-fp-is-a-prime-ideal}{HERE}.

See Kemper's \cite{kemper2011course}, Lemma 1.22 on Page 17, which completely described prime and maximal ideals in quotients.

\section{Definition. Height}

Here the definition \textit{height} is specifically for prime ideal $\mathfrak p \vartriangleleft_{pr} R$ for some ring $R$. For a general definition, see a post \href{https://math.stackexchange.com/questions/2689141/definition-of-height-of-an-ideal}{HERE}; see a webpage \href{https://encyclopediaofmath.org/wiki/Height_of_an_ideal}{HERE}; or see \cite{kemper2011course} Definition 6.10 on Page 68.

Nagata's example: Notherian ring with infinite Krull dimension, see \href{https://math.stackexchange.com/questions/1109732/noetherian-ring-with-infinite-krull-dimension-nagatas-example}{HERE} and a post \href{https://mathoverflow.net/questions/21067/noetherian-rings-of-infinite-krull-dimension?_gl=1*1kwuhw1*_ga*MzA3ODU1MDgwLjE2OTY5Nzg1OTg.*_ga_S812YQPLT2*MTY5Njk3ODU5Ny4xLjEuMTY5Njk4MDUwNS4wLjAuMA..}{HERE}.

\section{Proposition 1.7.}

Difference between algebraic set and affine algebraic set? See \href{https://math.stackexchange.com/questions/3486407/difference-between-algebraic-set-and-affine-algebraic-set-in-hartshorne}{HERE}.

For an analogue in Projective, see Exercise 2.6 \ref{} in Chapter 1.2. And a post \href{https://math.stackexchange.com/questions/670156/hartshorne-exercise-2-6}{HERE}.

\section{Theorem 1.8A.}

For transcendence degree, see \href{https://en.wikipedia.org/wiki/Transcendental_extension#CITEREFMilne}{HERE} and a \href{https://www.jmilne.org/math/CourseNotes/FT.pdf}{NOTE} by Milne James.

\section{Proposition 1.10.}

Apart from the proof, we discussed \textit{locally closed subset}.
See \href{https://en.wikipedia.org/wiki/Locally_closed_subset}{HERE} for its equivalent definitions.

\section{Proposition 1.13.}

See \href{https://math.stackexchange.com/questions/1292811/help-with-proposition-1-13-in-hartshornes-algebraic-geometry}{HERE}.

\section{Exercise 1.1.}

\subsection{(a)}

By definition of affine coordinate ring we have 
\[A(Y)=A/I(Y)=A/I(Z(f))=A/\sqrt{\langle f\rangle}.\]
While $f$ is irreducible in U.F.D. $k[x,y]$, the ideal it generated will be a prime ideal, which is radical. Therefore we can further simplify the expression as 
\[A/\sqrt{\langle f\rangle}=A/\langle f\rangle=k[x,y]/\langle y-x^2\rangle=k[x].\]
Hence we can conclude $A(Y)$ is isomorphic to a polynomial ring in one variable over $k$.

\subsection{(b)}

\section{Exericse 1.2.}

My initial guess was incorrect, in which I thought $I(Y)=\langle z-xy\rangle$.

\subsection{}

See a post \href{https://math.stackexchange.com/questions/1864637/the-affine-coordinate-ring-of-twisted-cubic-curve-y-is-ay-kx-y-z-z-x3}{HERE}.

The correct one is $I(Y)=\langle z-x^3,~ z-y^2\rangle$.
Notice that \[\operatorname{dim}Y=\operatorname{dim}A(Y)=\operatorname{dim}k[x,y,z]/\langle z-x^3,~ z-y^2\rangle=\operatorname{dim}k[z]=\operatorname{tr.deg}_k k(z)=1.\]
Therefore we proved that $A(Y)$ is isomorphic to a polynomial ring in one variable over $k$.

Question: How to compute $I(\cdot)$ precisely?

\section{Exercise 1.4.}

See a post \href{https://math.stackexchange.com/questions/128102/why-is-the-zariski-topology-on-bbb-a2-not-the-product-topology-on-bbb-a1}{HERE}, \href{https://math.stackexchange.com/questions/2119539/proving-that-the-zariski-topology-in-mathbba2-is-not-the-product-topology}{HERE},
and \href{https://math.stackexchange.com/questions/1607060/show-that-the-zariski-topology-on-a2-is-not-the-product-topology-on-a1-tim}{HERE}.

The hint was to consider diagonal. Let the coordinate ring of $\mathbb A^2$ be $A(\mathbb A^2)=k[x,y]$ where $k$ is algebraically closed. 
Then the diagonal \[\Delta =\{(x,y)\in\mathbb A^2 ~\mid~ x=y\}= Z(x-y=0)\] is closed in Zariski topology of $\mathbb A^2$.

But it cannot be countably many union of closed subsets in product topology of copies of Zariski topology on $\mathbb A^1$, which are finitely many points. \todo{Wrong!}

Here we used the fact that $k$ is infinite given it's algebraically closed.

\subsection{}

See the first post!
Closed subset of product topology on $\mathbb A^1\times \mathbb A^1$ can be uncountable, for example, a line $\{(x_0,y)\in\mathbb A^1\times A^1 ~\mid~ y\in k\}$ where $x_0\in k$ is fixed would be closed. But it's uncountable. 

The reason why $\Delta$ is closed in Zariski topology of $\mathbb A^2$ is correct. 

For product topology, the reason why it's not closed is because Zariski topology on $\mathbb A^1$ is not Hausdorff, by a lemma we mentioned we know $\Delta$ isn't closed. \todo{Verified!}

